\documentclass[11pt,letterpaper,sans]{moderncv}
\usepackage{cv}
\usepackage{comment}
\begin{document}

\recipient{Boston Dynamics}{78 Fourth Avenue\\Waltham, MA\\0241-7507, USA}
\date{September 29, 2012}
\opening{Dear Sir or Madam,}
\closing{Sincerely,}
%\enclosure{curriculum vit\ae{}}
\makelettertitle

I came across the job posting for a Control Systems Engineer and I believe that I am a perfect fit for this position at Boston Dynamics. As a graduate student at the University of Waterloo, I have spent the last two years designing and building a 14DOF lower body humanoid robot for research in bipedal locomotion. My responsibilities for this project included the complete mechanical design in CAD, drivetrain selection through dynamic simulations, electromechanical assembly/testing and feedback controller design to achieve walking (in simulation). This hardware was designed to provide a platform for my thesis, which presents a novel walking control strategy focused on foot placement for robust and energetically efficient gait synthesis. 

Throughout my university career, I have gained a wide range of theoretical knowledge and practical skills required for this position. On the theoretical side, I excelled at various courses in the field of advanced mechanics (kinematics, dynamics), robotics (state estimation, trajectory planning, etc) and control theory (analog, digital, etc). Through various coop placements in R\&D engineering labs, I also gained the practical skills required to design, debug and test complex hardware aimed for real world applications. These skills and knowledge culminated in my fourth year design project, where my vision was to build a thought-controlled wheelchair. I led a group of fourth year engineering students to successfully build a functional prototype with limited resources in 8 months. My team ultimately came in first place amongst 50+ engineering design teams and won the annual design cup challenge prize.

In addition to my academic and working experience, I have strong interpersonal and communication skills. Shortly after my success with the design project, I was invited to speak at a renowned TEDx event. I strongly believe that my passion for building solutions to complex engineering problems is evident in this talk. If interested, I would like to invite you to learn more about some of the projects I have been involved with or to watch the talk at \href{http://cv.safwanc.com}{http://cv.safwanc.com}. 

Thank you for your time and consideration.

\makeletterclosing

\end{document}